Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries. Among FEM-based formulations for porous media flows, the control volume finite element method~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements. In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are interpolated with CV basis functions~\citep{voller_2009}.

>>>>

The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries. Among FEM-based formulations for porous media flows, the control volume finite element method~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use geometry-conforming elements (\eg triangles, tetrahedra, pyramids etc). In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are interpolated with CV basis functions~\citep{voller_2009}.
